Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-03 android-stacks.tex
all over

After distilling the information available on the exception stack traces we could find 
the the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:topten} illustrates the top 10 root causes found in the study,
 ranked by the number of distinct project repositories on which they were reported. 
The table shows: the number of times each exception was reported as 
the root cause of a stack trace, the number of distinct projects reporting such causes on stack traces, 
and the percentages of such in relation to all reported exceptions and analyzed projects respectively.
It also presents the whether the method responsible for signaling the exceptions were
part of Android, the application itself, libcore, or a third-party library as presented in Table  \ref{tab:signalers}

@@

We can observe that most of this set is composed by exceptions defined by java.lang,
which are mostly not explicitly thrown by the developer but include
the exceptions implicitly thrown by the JVM due to programming errors 
(e.g., out-of-bounds array index, division-by-zero, access to a null reference)
 or resource limitation (e.g., OutOfMemoryError).
For such exceptions, which represent programming bugs or resource limitations, 
there is usually no proper handling besides presenting an error message to
 the user and restarting the application. Only high fault tolerant systems need to 
provide solutions to handle them. Hence, the best strategy to deal with them
is try to prevent them.

\emph{\textbf{The high number of NullPointerExceptions.}}
From this set the java.lang.NullPointerException was the most reported root cause; 27,71\% 
of the analyzed exception stack traces reported a java.lang.NullPointerException the root cause. 
Considering the frequencly of NullPointerException across projects, we could observe that
 51,96\% of all projects reported at least one exception stack trace on which the NullPoiterException
was the root cause.
 The NullPointerExceptions are mainly signaled inside the applicaiton code and the Android platform,
 although we also find NullPointerExceptions being signaled from third-party libraries. Regarding
reusable code, there is no consensus whether it is a good or bad practice to 
re-throw a NullPointerException. Some prefer to encapsulate such an exception on
IllegalArgumentException, while others~\cite{bloch2008effective} argue that the
NullPointerException makes the cause of the problem explicit and hence 
should not be wrapped.

>>>>

After distilling the information available on the exception stack traces we could find 
the the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:topten} illustrates the top 10 root causes found in the study,
 ranked by the number of distinct project repositories on which they were reported. 
The table shows how many times method responsible for signaling the exceptions were
part of Android Platform, the application itself, libcore, or a third-party library as presented in Table  \ref{tab:signalers}

@@

We can observe that most of this set is composed by exceptions defined by java.lang,
which are mostly implicitly thrown by the JVM due to programming mistakes 
(e.g., out-of-bounds array index, division-by-zero, access to a null reference)
 or resource limitation (e.g., OutOfMemoryError).
For such exceptions there is usually no proper handling besides presenting an error message to
 the user and restarting the application. Only high fault tolerant systems need to 
provide solutions to handle them.

\emph{\textbf{The high number of NullPointerExceptions.}}
From this set the java.lang.NullPointerException was the most reported root cause (27,71\% )
Considering the frequencly of NullPointerException across projects, we could observe that
 51,96\% of all projects reported at least one exception stack trace on which the NullPoiterException
was the root cause.
 The NullPointerExceptions are mainly signaled inside the applicaiton code and the Android platform,
 although we also find NullPointerExceptions being signaled from third-party libraries. Regarding
reusable code, there is no consensus whether it is a good or bad practice to 
re-throw a NullPointerException. Some prefer to encapsulate such an exception on
IllegalArgumentException, while others~\cite{bloch2008effective} argue that the
NullPointerException makes the cause of the problem explicit and hence 
should not be wrapped.
